---
title: "Homework 6"
author: "Caroline Andy"
date: "12/6/2020"
output: html_document
---

### Problem 1

```{r load, warning = FALSE, message = FALSE}
library(purrr)
library(tidyverse)
library(stringr)
library(patchwork)
library(skimr)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r}
#generate homicide table and summarize solved and unsolved murders by state
urlfile = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide = read_csv(url(urlfile)) %>%
  mutate(city_state = str_c(city, state, sep = "_"),
         victim_age = as.numeric(victim_age),
         resolution = case_when(
           disposition %in% "Closed without arrest" ~ 1,
           disposition %in% "Closed by arrest" ~ 0, 
           disposition %in% "Open/No arrest" ~ 0)) %>%
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa_AL") %>%
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide %>%
  filter(city_state == "Baltimore_MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df, 
    family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
) %>%
  select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
model_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Problem 2

Make 3 models (2 specified, 1 that is our choice) and compare them. Can pick and choose variables to include in model (if we specify why). 


```{r, message = FALSE, warning = FALSE}
bweight = read_csv("./birthweight.csv")
skim(bweight) 
# no missing values, all variables are numeric

bweight = bweight %>%
  mutate(babysex = (fct_infreq(as.factor(babysex))),
         frace = (fct_infreq(as.factor(frace))),
         mrace = (fct_infreq(as.factor(mrace))),
         malform = (fct_infreq(as.factor(malform)))) 

## function for backward stepwise selection
mult.fit <- lm(bwt ~ ., data = bweight)
step(mult.fit, direction = 'backward')

reg = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + 
    mheight + mrace + parity + ppwt + smoken, data = bweight)

reg %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

We can graph residuals against x values to see if there are any trends in residuals (ie. low x values tend to have higher residuals, etc) 

Show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r, message = FALSE, warning = FALSE}
bweight = modelr::add_residuals(bweight, reg)
modelr::add_predictions(bweight, reg) %>%
  ggplot(aes(x = resid, y = pred)) + geom_point()
```

Compare models to two models:
- One using length at birth and gestational age as predictors 
- One using head circumference, length, sex and all interactions as predictors (for interactions can just do: circumference*length*sex)

```{r, message = FALSE, warning = FALSE}
## Predictors = length and gesitational age 
length_gest = lm(bwt ~ blength + gaweeks, data = bweight)
length_gest %>%
  broom::glance()
summary(length_gest)
## Adjusted R squared = 0.5767

## Predictors = head circumference, length, sex and all interactions
length_circ_sex = lm(bwt ~ blength*bhead*babysex, data = bweight)
length_circ_sex %>%
  broom::glance()
summary(length_circ_sex)
## Adjusted R squared = 0.6844 
```

```{r, message = FALSE, warning = FALSE}
cv_df = 
  crossv_mc(bweight, 4342) 
train = cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
test = cv_df %>% pull(test) %>% .[[1]] %>% as_tibble

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    my_mod  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + 
    mheight + mrace + parity + ppwt + smoken, data = .x)),
    length_ga_mod  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    length_circ_sex_mod = map(train, ~lm(bwt ~ blength*bhead*babysex, data = .x))) %>% 
  mutate(
    rmse_mymod = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
    rmse_length_ga_mod = map2_dbl(length_ga_mod, test, ~rmse(model = .x, data = .y)),
    rmse_length_circ_sex_mod = map2_dbl(length_circ_sex_mod, test, ~rmse(model = .x, data = .y)))
```

```{r, message = FALSE, warning = FALSE}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

### Problem 3

```{r message = FALSE, warning = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

# regression model for 1 (weather_df) sample
lm(tmax ~ tmin, data = weather_df) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r, message = FALSE, warning = FALSE}
# draw one bootstrap sample
boot_sample = function(df) {
  sample_frac(weather_df, replace = TRUE)
}

# draw 5000 bootstrap samples
boot_straps = 
  data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )

# running regression models using 5000 bootstrap samples 
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(strap_number, results) %>% 
  unnest(results) 

# find mean r squared
bootstrap_results %>%
  summarize(mean_r_sq = mean(r.squared))
```


```{r, message = FALSE, warning = FALSE}


```