---
title: "Homework 6"
author: "Caroline Andy"
date: "12/6/2020"
output: html_document
---

### Problem 1

```{r load, warning = FALSE, message = FALSE}
library(purrr)
library(tidyverse)
library(stringr)
library(patchwork)
library(skimr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r}
#generate homicide table and summarize solved and unsolved murders by state
urlfile = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide = read_csv(url(urlfile)) %>%
  mutate(city_state = str_c(city, state, sep = "_"),
         victim_age = as.numeric(victim_age),
         resolution = case_when(
           disposition %in% "Closed without arrest" ~ 1,
           disposition %in% "Closed by arrest" ~ 0, 
           disposition %in% "Open/No arrest" ~ 0)) %>%
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa_AL") %>%
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df = 
  homicide %>%
  filter(city_state == "Baltimore_MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df, 
    family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
model_results_df = 
  homicide %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
) %>%
  select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(city_state, term, OR, starts_with("CI"))
```

```{r}
model_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Problem 2

Make 3 models (2 specified, 1 that is our choice) and compare them. Can pick and choose variables to include in model (if we specify why). 

Note:
we can graph residuals against x values to see if there are any trends in residuals (ie. low x values tend to have higher residuals, etc) 

```{r, message = FALSE, warning = FALSE}
bweight = read_csv("./birthweight.csv")
skim(bweight) 
# no missing values, all variables are numeric

bweight = bweight %>%
  mutate(babysex = (fct_infreq(as.factor(babysex))),
         frace = (fct_infreq(as.factor(frace))),
         mrace = (fct_infreq(as.factor(mrace))),
         malform = (fct_infreq(as.factor(malform)))) 

reg = lm(bwt ~ blength + gaweeks + malform + pnumlbw + smoken + mrace + parity, data = bweight)
reg %>% 
  broom::glance()
summary(reg)

reg2 = lm(bwt ~ ., data = bweight)
reg2 %>% 
  broom::glance()
summary(reg2)

library(leaps)
b<-regsubsets(bwt ~ ., data=bweight)
   (rs<-summary(b))

## function for backward stepwise selection
mult.fit <- lm(bwt ~ ., data=bweight)
step(mult.fit, direction='backward')

reg3 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + 
    mheight + mrace + parity + ppwt + smoken, data=bweight)
reg3 %>%
  broom::glance()
summary(reg3)

reg3 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```


Compare models to two models:
- One using length at birth and gestational age as predictors 
- One using head circumference, length, sex and all interactions as predictors (for interactions can just do: circumference*length*sex)

```{r, message = FALSE, warning = FALSE}
## Predictors = length and gesitational age 
length_gest = lm(bwt ~ blength + gaweeks, data = bweight)
length_gest %>%
  broom::glance()
summary(length_gest)
## Adjusted R squared = 0.5767

## Predictors = head circumference, length, sex and all interactions
length_circ_sex = lm(bwt ~ blength*bhead*babysex, data = bweight)
length_circ_sex %>%
  broom::glance()
summary(length_circ_sex)
## Adjusted R squared = 0.6844 
```